map_enclosure_sites

### 2024-09-11 smelt_2019_winterspring/map_enclosure_sites.Rmd
updates to figures for resubmission of 2019 synthesis paper

```{r}
library(viridis)
library(sf)
library(dplyr)
library(ggplot2)
library(spData)
library(here)
library(readr)
library(janitor)
library(deltamapr)
library(cowplot)
library(ggspatial)

@@

stations_sf <- st_as_sf(latlon, coords = c("Longitude", "Latitude"), crs = 4326)
data("us_states", package = "spData")
California = dplyr::filter(us_states, NAME == "California")
stations_sf_4269 <- st_transform(stations_sf, crs = st_crs(California))
WW_Watershed_4269 <- st_transform(WW_Watershed, crs = st_crs(California))
```

```{r}
(smelt_map <- ggplot() +
    geom_sf(data = WW_Watershed_4269, fill = "gray80", colour = "gray80", alpha = 0.8, inherit.aes = FALSE) +
    geom_sf(data = stations_sf_4269, inherit.aes = FALSE, size = 4, color = "black")+
   geom_sf_label(data = stations_sf_4269, aes(label = factor(Location)), inherit.aes = FALSE, size = 4, color = "black",
                 nudge_x = c(-0.08, -0.05),
                 nudge_y = c(0.01, -0.03))+
    annotate(geom = "text", x = -121.75, y = 38.10, size = 3.2, label = "Sacramento River", fontface = "italic",angle = 36) +
    annotate(geom = "text", x = -121.62, y = 38.09, size = 3.2, label = "San Joaquin River", fontface = "italic", angle = 10) +
    annotate(geom = "text", x = -121.96, y = 38.07, size = 3.2, label = "Suisun Bay", fontface = "italic") +
    annotate(geom = "text", x = -121.68, y = 38.26, size =3.2 , label = "Liberty Island", fontface = "italic") +
    scale_x_continuous(limits = c(-122.2, -121.45)) +
  scale_y_continuous(limits = c(37.95, 38.4))+
    annotation_north_arrow(location = "tr", which_north = "true",
                           pad_x = unit(.005, "in"), pad_y = unit(0.15, "in"),
                           style = north_arrow_fancy_orienteering) +
    annotation_scale(location = "bl", bar_cols = c("darkgray", "white", "darkgray", "white"), text_cex = 1.1)+
  theme_bw() +
    theme(axis.title = element_blank(),
        axis.text = element_text(size = 13) ,
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 0.5, vjust = 0.5)))
```

```{r}
insetbbox = st_bbox(c(xmin = -122.2, xmax = -121.45, ymax = 37.95, ymin = 38.4), crs = st_crs(4326))
box_sf <- st_as_sfc(insetbbox)

(inset <- ggplot() +
    geom_sf(data = California, fill = "white") +
    geom_sf(data = WW_Delta, colour = "steelblue4", size = 0.3) +
    geom_sf(data = box_sf, fill = NA, color = "red", size = 0.5) +

    theme_bw() +
    theme(axis.text = element_blank(),
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()))
```

```{r}
(gg_inset_map = ggdraw() +
   draw_plot(smelt_map) +
   draw_plot(inset, x = 0.1, y = 0.63, width = 0.26, height = 0.31))
```

@@

>>>>

```{r}
library(viridis)
library(sf)
library(dplyr)
library(ggplot2)
library(spData)
library(here)
library(readr)
library(janitor)
library(deltamapr)
library(cowplot)
library(ggspatial)
library(basemaps)

@@

stations_sf <- st_as_sf(latlon, coords = c("Longitude", "Latitude"), crs = 4326) 
data("us_states", package = "spData")
California = dplyr::filter(us_states, NAME == "California")
stations_sf_4269 <- st_transform(stations_sf, crs = 4269) %>%
  arrange(Location) %>%
  mutate(Location = factor(Location))
WW_Watershed_4269 <- st_transform(WW_Watershed, crs = 4269)
```

```{r}

smelt_map <- ggplot() +
    geom_sf(data = WW_Watershed_4269, fill = "azure2", colour = "gray60", alpha = 0.8, inherit.aes = FALSE) +
      annotate(geom = "text", x = -121.75, y = 38.10, size = 3.2, label = "Sacramento River", fontface = "italic",angle = 36) +
    annotate(geom = "text", x = -121.62, y = 38.09, size = 3.2, label = "San Joaquin River", fontface = "italic", angle = 10) +
    annotate(geom = "text", x = -121.96, y = 38.07, size = 3.2, label = "Suisun Bay", fontface = "italic") +
    annotate(geom = "text", x = -121.68, y = 38.26, size =3.2 , label = "Liberty \nIsland", fontface = "italic") +  geom_sf(data = stations_sf_4269, inherit.aes = FALSE, size =4, aes(shape = Type, fill = Type, size = Type))+
  scale_shape_manual(values = c(21,22))+
  scale_fill_manual(values = c("darkblue","wheat"))+
   geom_sf_label(data = stations_sf_4269, aes(label = Location), inherit.aes = FALSE, size = 4, color = "black",
                 nudge_x = c(0.03, 0.04, 0.03, 0.03, 0.05, -0.04, -0.03, -0.04),
                 nudge_y = c(0.025, 0.03,0.02, 0.025, 0.02, -0.02, -0.03, -0.01))+

    scale_x_continuous(limits = c(-122.2, -121.45)) +
  scale_y_continuous(limits = c(37.8, 38.5))+
    annotation_north_arrow(location = "tr", which_north = "true",
                           pad_x = unit(.005, "in"), pad_y = unit(0.15, "in"),
                           style = north_arrow_fancy_orienteering) +
    annotation_scale(location = "bl", bar_cols = c("darkgray", "white", "darkgray", "white"), text_cex = 1.1)+
  theme_bw() +
    theme(axis.title = element_blank(),
        axis.text = element_text(size = 13) ,
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 0.5, vjust = 0.5),
        legend.position = "none")
smelt_map
```

```{r}
Cali = st_transform(California, crs = 3857)

extbb = st_bbox(Cali)

basem = basemap_gglayer(
  ext = extbb,
  map_service = "osm",
  map_type = "topographic",
  alpha = 0.5
)

ggplot() + basem+
  theme(legend.position = "none")+
  scale_fill_manual(values = sort(unique(basem$data$fill)))

insetbbox = st_bbox(c(xmin = -122.2, xmax = -121.45, ymax = 37.95, ymin = 38.4), crs = st_crs(4326)) 
box_sf <- st_as_sfc(insetbbox) %>%
  st_transform(crs = 3857)

inset <- ggplot() +
    basem+
    geom_sf(data = Cali, fill = "white", alpha = 0.1, linewidth =.7) +
   geom_sf(data = WW_Delta, colour = "grey60", linewidth = 0.3) +
    geom_sf(data = box_sf, fill = NA, color = "black", linewidth = .7) +

    theme_bw() +
    theme(axis.text = element_blank(),
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.position = "none")+
  scale_fill_manual(values = sort(unique(basem$data$fill)))+
  annotation_scale()+
  annotation_north_arrow(location = "tr")+
  annotate("text", label = "California", x = -13600000, y = 5000000, size = 5, fontface = "italic")+
  annotate("text", label = "United States\n of America", x = -13000000, y = 4800000, size = 6, fontface = "italic")+
  annotate("text", label = "Study Area",x = -13600000, y = 4700000, size = 3, fontface = "bold" )

inset
```

```{r}
(gg_inset_map = ggdraw() +
   draw_plot(smelt_map) +
   draw_plot(inset, x = 0.1, y = 0.63, width = 0.26, height = 0.31))

gg_inset_map
```

@@

Or we can plot them one next to the other to satisfy the pesky reviewer

```{r}

library(patchwork)

inset+ smelt_map+ plot_layout(ncol =2, widths = c(1,2))

tiff(filename = here::here("smelt_2019_allseasons",  "figures", "map_sites.tiff"), width = 10, height = 7, units = "in", pointsize = 12, family = "sans", res = 300, compress = "lzw")

inset+ smelt_map+ plot_layout(ncol =2, widths = c(1,2))
dev.off()

pdf(file = here::here("smelt_2019_allseasons",  "figures", "map_sites.pdf"), width = 10, height = 7,  pointsize = 12,   compress = "lzw")

inset+ smelt_map+ plot_layout(ncol =2, widths = c(1,2))
dev.off()

```
